\begin{acknowledgements}
I would firstly like to thank my supervisors Peter Gallagher and Eoin Carley. Your guidance and support throughout my PhD has been constant and has saved me from sounding foolish on more than one occasion. It has been a pleasure working with you both over the last four years.

Operations at I-LOFAR, and my understanding thereof, would not be where they are today without Joe McCauley. Thank you for always being on hand to troubleshoot failed observations.

Brian Coghlan was an invaluable resource during the installation of REALTA and the development of recording data from the Transient Buffer Boards at I-LOFAR. I am grateful for your patience while I was finding my feet as a PhD student. 

I want to express my gratitude to Sophie Murray and Shane Maloney. You've opened my eyes to the wonderful world of open source software and ``basic version control techniques". Thank you, also, for many great ideas from many long group meetings.

I have been incredibly lucky to spend some of my time as a PhD student in a place as steeped in myth as the astrophysics student office at Trinity College Dublin. Here I met some amazing people who I am truly honoured to call friends. Laura Hayes and Aoife McCloskey, you are both everything I aspire to be as a scientist and as a person. Thank you for making me feel welcome from the moment I first walked into the office.
D\'ualta \'O Fionnag\'ain and Ioana Boian, I still find it hard that I don't see you every day. Thank you both for many geography quizzes and to D\'ualta in particular for getting me interested in, and subsequently losing money to, cryptocurrencies.
To Rob Kavanagh, Stephen Carolan, Eoin Farrell and Amanda Mesquita. Although our time together was cut short by a move to a new institute you are all part of the many great memories I made throughout the last four years.
To Tadhg Garton, thank you for being a wall to bounce ideas off and introducing me to your slightly worrying sense of humour/coping mechanism.

%Thank you also to Donna, Gopal, Carolina and Ankit 
During my PhD I have had the fortune to share my time with many wonderful people at the Dublin Institute for Advanced Studies (\#DIASDiscovers). There are too many to name but I'm going to try anyway. Alberto, Anton, David, Eoin, Jeremy, Johnny, Maria K, Maria M, Mario, Ruben, Sam and Shilpi.

I started this PhD in the company of four people who have made the last four years incredibly enjoyable. Laura Murphy, Brendan Clarke, Aoife Ryan and Ciara Maguire, sharing this journey with you has been a blessing. I don't know how I would have made it this far without you all, thank you.
In particular I want to thank Aoife and Ciara for answering my almost constant stream of questions about radio interferometry and for putting up with impromptu drum solos on my desk.

My thanks also go to Conor, Marlon, John, Dan, the former residents of 40 Greenmount Road and the Mullinguardians of the Galaxy.

To my family Noel and Siobhan, Conor and \'Eadaoin. Thank you for everything. Your love and support has brought me to where I am today and I am eternally grateful for that.

Finally I want to say thank you to Camille Stock. Despite having written tens of thousands of words to describe solar radio physics, I don't know what to say to express how much you mean to me. In the most bleak moments of writing this thesis you have picked me up off the floor both metaphorically and literally. I am incredibly lucky to be loved by someone as generous, kind and caring as you. Thank you.

\end{acknowledgements}
