\chapter{List of Publications}
\label{chapter:publications}
%
\begin{singlespace}
\vspace{-5mm}

%
%\section*{Oral Presentations}
%\begin{enumerate}
%STELLAR Space Weather Workshop
%Virtual
%12th - 15th July 2021
%
%\item \textit{LOFAR Single Station Radio Data Analysis Tutorial}
%I-LOFAR Science and Techniques Workshop
%I-LOFAR Education Centre, Birr Castle, Co. Offaly, Ireland
%2nd - 4th March 2020
%
%Scattering of Radio Waves in the Solar Corona
%I-LOFAR Science and Techniques Workshop
%I-LOFAR Education Centre, Birr Castle, Co. Offaly, Ireland
%2nd - 4th March 2020
%
%Single Station Data Analysis Tutorial
%Young European Radio Astronomers Conference
%Dublin Institute for Advanced Studies/Trinity College Dublin, Ireland
%26th - 29th August 2019
%
%Interferometric Imaging of Type III Bursts in the Solar Corona
%Community of European Solar Radio Astronomers Workshop
%Leibniz-Institut für Astrophysik Potsdam, Germany
%8th - 12th July 2019
%
%Interferometric Imaging of Type III Bursts in the Solar Corona
%\item \textit{Finding Fast Solar Radio Transients in I-LOFAR Transient Buffer Board Data},\\ Irish National Astronomy Meeting (INAM), 2018
%\item \textit{Finding Fast Solar Radio Transients in I-LOFAR Transient Buffer Board Data},\\ Community of European Solar Radio Astronomers (CESRA) Summer School, 2018
%\end{enumerate}
%
%%
%\section*{Poster Presentations}
%\begin{enumerate}
%\item \textit{The Irish LOw Frequency ARray (I-LOFAR)}, \\ International Workshop on Solar, Heliospheric and Magnetospheric Radioastronomy, 2017
%\\ DOI: \url{https://doi.org/10.6084/m9.figshare.5572660.v1}
%\item \textit{Nanosecond Sampling of the Radio Sky with I-LOFAR's Transient Buffer Boards (TBB)}, \\ 17th RHESSI (Reuven Ramaty High Energy Solar Spectroscopic Imager) Workshop, 2018
%\\ DOI: \url{https://doi.org/10.6084/m9.figshare.6669173.v1}
%\end{enumerate}
%
%
%%
%\section*{Workshops \& Conferences Attended}
%\begin{enumerate}
%\item INAM, Maynooth University, 2017
%\item International Workshop on Solar, Heliospheric and Magnetospheric Radioastronomy, Observatoire de Paris, 2017
%\item I-LOFAR User's Data Workshop, University College Dublin, 2018
%\item 17th RHESSI Workshop, Trinity College Dublin, 2018
%\item Astro Hack Week, Lorentz Cetnre, Leiden University, 2018
%\item INAM, Birr Theatre, Birr, Co. Offaly, 2018
%\item CESRA Summer School, Observatoire Royal de Belgique, 2018 
%\item LOFAR Data Processing School, Netherlands Institute for Radio Astronomy (ASTRON), 2018
%\end{enumerate}

\section*{Publications}
\begin{enumerate}
\item Corentin K. Louis, Caitriona M. Jackman, Jean-Mathias Griessmeier, Olaf Wucknitz, David. J. McKenna, \textbf{Pearse C. Murphy}, Peter T. Gallagher, Eoin Carley, Dúalta Ó Fionnagáin, Aaron Golden, Joe McCauley, Paul Callanan, Matt Redman, Christian Vocks.
\\``Observing Jupiter's radio emissions using multiple LOFAR stations: a first case study of the Io-decametric emission using the Irish IE613, French FR606 and German DE604 stations"
\\ \textit{Royal Astronomical Society Techniques and Instruments journal} (2021 submitted)
\item \textbf{P. C. Murphy}, P. Callanan, J. McCauley, D. J. McKenna, D. Ó Fionnagáin, C. K. Louis, M. P. Redman, L. A. Cañizares, E. P. Carley, S. A. Maloney, B. Coghlan, M. Daly, J. Scully, J. Dooley, V. Gajjar, C. Giese, A. Brennan, E. F. Keane, C. A. Maguire, J. Quinn, S. Mooney, A. M. Ryan, J. Walsh, C. M. Jackman, A. Golden, T. P. Ray, J. G. Doyle, J. Rigney, M. Burton, P. T. Gallagher.
\\``First Results from the REAL-time Transient Acquisition backend (REALTA) at the Irish LOFAR station",
\\ \textit{Astronomy and Astrophysics} Volume 655, A16 (2021)
\item A. M. Ryan, P. T. Gallagher, E. P. Carley, M. A. Brentjens,\textbf{ P. C. Murphy}, C. Vocks, D. E. Morosan, H. Reid, J. Magdalenic, F. Breitling, P. Zucca, R. Fallows, G. Mann, A. Kerdraon, R. Halfwerk.
\\``LOFAR imaging of the solar corona during the 2015 March 20 solar eclipse",
\\ \textit{Astronomy and Astrophysics}, Volume 648, A43 (2021)
\item \textbf{Pearse C. Murphy}, Eoin P. Carely, Aoife Maria Ryan, Pietro Zucca, Peter T. Gallagher.
\\ ``LOFAR Observations of Radio Burst Source Sizes and Scattering in the Solar Corona",
\\ \textit{Astronomy and Astrophysics}, Volume 645, A11 (2021)
\item Vishal Gajjar, Andrew Siemion, Steve Croft, Bryan Brzycki, Marta Burgay, Tobia Carozzi, Raimondo Concu, Daniel Czech, David DeBoer, Julia DeMarines, Jamie Drew, J. Emilio Enriquez, James Fawcett, Peter Gallagher, Michael Gerret, Nectaria Gizani, Greg Hellbourg, Jamie Holder, Howard Isaacson, Sanjay Kudale, Brian Lacki, Matthew Lebofsky, Di Li, David H. E. MacMahon, Joe McCauley, Andrea Melis, Emilio Molinari, \textbf{Pearse Murphy}, Delphine Perrodin, Maura Pilia, Danny C. Price, Claire Webb, Dan Werthimer, David Williams, Pete Worden, Philippe Zarka, and Yunfan Gerry Zhang.
\\``The Breakthrough Listen Search for Extraterrestrial Intelligence ",
\\ \textit{Astro2020: Decadal Survey on Astronomy and Astrophysics, APC white papers, no. 223; Bulletin of the American Astronomical Society}, Vol. 51, Issue 7, id. 223 (2019)
\item David M. Long, \textbf{Pearse C. Murphy}, Georgina Graham, Eoin P. Carley, David P\'{e}rez-Su\'{a}rez.
\\ ``A Statistical Analysis of the Solar Phenomena Associated with Global EUV Waves",
\\ \textit{Solar Physics}, Volume 292 , Issue 185, (2017).
%Long, D.M., \textbf{Murphy, P. C.}, Graham, G. et al. Sol Phys (2017) 292: 185. \doihttps{https://doi.org/10.1007/s11207-017-1206-0}
\end{enumerate}




\end{singlespace}

